Evaluation of the article

### 2024-11-18 pages/paper_evaluation.qmd
feat(paper evaluation): add mean of scores

@@

  # Calculating some reporting quality scores
  scores = calculate_scores(df).rename_axis('study').reset_index()
  display(scores)

>>>>

With similar conclusions from `score` and `score_fully`, I think it's sensible to present `score_fully` as that is the simplest interpretation.

@@

  # Calculating some reporting quality scores
  scores = calculate_scores(df).rename_axis('study').reset_index()
  display(scores)
  print("Mean values...")
  display(scores.apply(pd.to_numeric, errors="coerce").mean())
